
# Model Fitting

Logistic regression is the appropriate model class for our binary response, where we want to model the probability that a record is for a readmission within 30 days.

```{r fit_data}
# revise indiv scores per aggregation in order to fit by covariates
snf_data_fit <- snf_data_a %>%
  mutate(CCI = ifelse(CCI > 14, 14, CCI),
         LACE = ifelse(LACE < 4, 4, 
                       ifelse(LACE > 18, 18, LACE)),
         HOSPITAL = ifelse(HOSPITAL > 11, 11, HOSPITAL))
```
  
## CCI 

The base model for readmission against CCI can be written as:  


$$
\begin{aligned}
log(\frac{p_{CCI_i}}{1-p_{CCI_{i}}}) &= \beta_0 + \beta_1  CCI_i \\
p_{CCI_{i}} &= \frac{e^{\beta_0 + \beta_1CCI_{i}}}{1 + e^{\beta_0 + \beta_1CCI_{i}}}
\end{aligned}
$$
where $i\ \epsilon\ [0, 14]$
  

```{r cci_base}
# Fit base model
CCI_mod0 <- glm(Readmit ~ CCI, family = binomial(link="logit"), data = snf_data_fit)

# get ests and confints
cci_b0 <- CCI_mod0$coefficients[1]
cci_b1 <- CCI_mod0$coefficients[2]
cci_confint <- confint(CCI_mod0)
cci_or <- exp(cci_b1)
cci_or_confint <- exp(cci_confint[2,])
```


The estimated model for probability of readmission can be estimated as:  

$$p_{CCI_i} = \frac{e^{-1.70 + 0.003*CCI_i}}{1+e^{-1.70 + 0.003*CCI_i}}$$


```{r cci_modplot}
CCI_plot0 <- glm(cbind(n.Readmit, n-n.Readmit) ~ CCI, family = binomial(link="logit"), data=readmit_cci)
x <- seq(0, 14, 0.1)
y <- exp(cci_b0 + cci_b1*x) / (1 + (exp(cci_b0 + cci_b1*x)))

y_025 <- exp(cci_confint[1,1] + cci_confint[2,1]*x) / (1 + (exp(cci_confint[1,1] + cci_confint[2,1]*x)))
y_975 <- exp(cci_confint[1,2] + cci_confint[2,2]*x) / (1 + (exp(cci_confint[1,2] + cci_confint[2,2]*x)))

cci_modline <- data.frame(x, y, y_025, y_975)

cci_fits <- data.frame(CCI = seq(0, 14, 1),
                       fit = fitted(CCI_plot0))

cci_rawdat <- snf_data_a %>%
  select(c(CCI, Readmit)) %>%
  mutate(Readmit = as.numeric(Readmit) - 1) %>%
  filter(CCI < 15)

cci_plt <- ggplot(readmit_cci, aes(CCI, p.Readmit)) +
  geom_point(alpha = 0.6, size = 4) + 
  geom_line(data=cci_modline, aes(x=x, y=y), alpha = 0.5) + 
  geom_line(data=cci_modline, aes(x=x, y=y_025), alpha = 0.5, lty = 2) + 
  geom_line(data=cci_modline, aes(x=x, y=y_975), alpha = 0.5, lty = 2) + 
  scale_y_continuous(breaks = seq(0, 0.5, 0.1), limits = c(0, 0.5)) + 
  scale_x_continuous(breaks = seq(0, 14, 2), limits = c(0, 14)) + 
  theme_minimal() + 
  labs(x = "CCI Score", y = "Probability of Readmission") +
  scale_shape_manual(name = "Legend",
                     breaks = c("Sample Readmit Rate", "Fitted Readmit Rate"),
                     values = c("Sample Readmit Rate"=1, "Fitted Readmit Rate"=15)) + 
  ggtitle(paste("Probability of Readmission by CCI: \nSample Readmission Rate + Fitted Model"))

suppressWarnings(print(cci_plt))
```


Full model diagnostics can be reviewed in [Appendix D](#AppendixD). No CCI + covariate models need to be fitted since we find no evidence that changes in CCI score are associated with changes in readmission risk.  
  
  
## LACE  

The base model for readmission against LACE can be written as:  
  
$$
\begin{aligned}
log(\frac{p_{LACE_i}}{1-p_{LACE_{i}}}) &= \beta_0 + \beta_1  LACE_i \\
p_{LACE_{i}} &= \frac{e^{\beta_0 + \beta_1LACE_{i}}}{1 + e^{\beta_0 + \beta_1LACE_{i}}}
\end{aligned}
$$
where $i\ \epsilon\ [4, 18]$  


```{r lace_mods}

# Fit base model
lace_mod0 <- glm(Readmit ~ LACE, 
                 family = binomial(link="logit"), data = snf_data_fit)

# Fit LACE and Patient Age
lace_age_mod <- glm(Readmit ~ LACE + PatientAge, 
                    family = binomial(link="logit"), 
                    data = snf_data_fit)

# LACE and Year
lace_yr_mod <- glm(Readmit ~ LACE + Year, 
                    family = binomial(link="logit"), 
                    data = snf_data_fit)

# LACE and Gender
lace_gen_mod <- glm(Readmit ~ LACE + Gender, 
                    family = binomial(link="logit"), 
                    data = snf_data_fit)

# LACE and Insurance Status
lace_ins_mod <- glm(Readmit ~ LACE + Insurance, 
                    family = binomial(link="logit"), 
                    data = snf_data_fit)
# LACE Additive Model
lace_add_mod <- glm(Readmit ~ LACE + PatientAge + Year + Gender + Insurance, 
                    family = binomial(link="logit"), 
                    data = snf_data_fit)

# Saturated LACE Model
lace_sat_mod <- glm(Readmit ~ LACE * PatientAge * Year * Gender * Insurance, 
                    family = binomial(link="logit"), 
                    data = snf_data_fit)

```

```{r lace_ests}
# get ests and confints
lace_b0 <- lace_gen_mod$coefficients[1]
lace_b1 <- lace_gen_mod$coefficients[2]
lace_b2 <- lace_gen_mod$coefficients[3]
lace_confint <- confint(lace_gen_mod)
lace_confint_p <- exp(lace_confint)/(1+exp(lace_confint))
```

The estimated odds for readmission based on LACE score is $e^{\hat{B_1}} = e^{0.150} = 1.162$, 95% CI: (1.137, 1.188); these results provide evidence that relative odds of readmission increasesexp() 11.7% - 22.1% for a one value increase in LACE score. The confidence intervals given are calculated with an quasibinomial overdispersion parameter $\phi = 4.26$ to account for extra-binomial variation present in the data. See [Appendix E](#AppendixE) for full model diagnostics.

The estimated model for probability of readmission can be estimated as:  

$$p_{LACE_i} = \frac{e^{-3.61 + 0.15*LACE_i + 0.34*Male_i}}{1+e^{-3.61 + 0.15*LACE_i + 0.34*Male_i}}$$
```{r lace_readmit_rename}
readmit_lace_gen <- readmit_lace_gen %>%
  rename(Gender = Value)
```


```{r lace_modplot}

x <- seq(4, 18, 0.1)

gen <- rep(c("Male", "Female"), each = 141)

y_male <- exp(lace_b0 + lace_b1*x + lace_b2) / (1 + (exp(lace_b0 + lace_b1*x + lace_b2)))
y_female <- exp(lace_b0 + lace_b1*x) / (1 + (exp(lace_b0 + lace_b1*x)))
y <- c(y_male, y_female)

ym_025 <- exp(lace_confint[1,1] + lace_confint[2,1]*x + lace_confint[3,1]) / (1 + (exp(lace_confint[1,1] + lace_confint[2,1]*x + lace_confint[3,1])))
ym_975 <- exp(lace_confint[1,2] + lace_confint[2,2]*x + lace_confint[3,2]) / (1 + (exp(lace_confint[1,2] + lace_confint[2,2]*x + lace_confint[3,2])))

yf_025 <- exp(lace_confint[1,1] + lace_confint[2,1]*x) / (1 + (exp(lace_confint[1,1] + lace_confint[2,1]*x)))
yf_975 <- exp(lace_confint[1,2] + lace_confint[2,2]*x) / (1 + (exp(lace_confint[1,2] + lace_confint[2,2]*x)))

y_025 <- c(ym_025, yf_025)
y_975 <- c(ym_975, yf_975)

two_x <- rep(x, times=2)
lace_modline <- data.frame(LACE = two_x, Gender = as.factor(gen), 
                           Fit = y, CI_lower = y_025, CI_upper = y_975)

lace_plt <- ggplot(lace_modline, aes(LACE, Fit)) + 
  geom_line() + 
  geom_line(aes(x=LACE, y=CI_lower), lty=2) + 
  geom_line(aes(x=LACE, y=CI_upper), lty=2) + 
  geom_point(data=readmit_lace_gen, aes(x=LACE, y=p.Readmit), alpha=0.6, size=3) + 
  scale_y_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1)) + 
  scale_x_continuous(breaks = seq(4, 18, 2), limits = c(4, 18)) + 
  theme_minimal() + 
  facet_wrap(vars(Gender)) + labs(x = "LACE Score", y = "Probability of Readmission") + 
  ggtitle(paste("Probability of Readmission by LACE: \nSample Readmission Rate + Fitted Model"))

suppressWarnings(print(lace_plt))
```  

  
  
## HOSPITAL  
  
The base model for readmission against HOSPITAL can be written as:  
  
$$
\begin{aligned}
log(\frac{p_{HOS_i}}{1-p_{HOS_{i}}}) &= \beta_0 + \beta_1  HOS_i \\
p_{HOS_{i}} &= \frac{e^{\beta_0 + \beta_1HOS_{i}}}{1 + e^{\beta_0 + \beta_1HOS_{i}}}
\end{aligned}
$$  
where $i\ \epsilon\ [0, 11]$  

```{r hos_mods}
# fit base model
hos_mod0 <- glm(Readmit ~ HOSPITAL, family=binomial(link="logit"), data = snf_data_fit)

# Fit HOS and Patient Age
hos_age_mod <- glm(Readmit ~ HOSPITAL + PatientAge, 
                    family = binomial(link="logit"), 
                    data = snf_data_fit)

# HOS and Year
hos_yr_mod <- glm(Readmit ~ HOSPITAL + Year, 
                    family = binomial(link="logit"), 
                    data = snf_data_fit)

# HOS and Gender
hos_gen_mod <- glm(Readmit ~ HOSPITAL + Gender, 
                    family = binomial(link="logit"), 
                    data = snf_data_fit)

# HOS and Insurance Status
hos_ins_mod <- glm(Readmit ~ HOSPITAL + Insurance, 
                    family = binomial(link="logit"), 
                    data = snf_data_fit)

# Additive HOS Model
hos_add_mod <- glm(Readmit ~ HOSPITAL + PatientAge + Year + Gender + Insurance, 
                    family = binomial(link="logit"), 
                    data = snf_data_fit)

# Saturated HOS Model
hos_sat_mod <- glm(Readmit ~ HOSPITAL * PatientAge * Year * Gender * Insurance, 
                    family = binomial(link="logit"), 
                    data = snf_data_fit)

```

```{r hos_coefs}
# get ests and confints
hos_b0 <- hos_gen_mod$coefficients[1]
hos_b1 <- hos_gen_mod$coefficients[2]
hos_b2 <- hos_gen_mod$coefficients[3]
hos_confint <- confint(hos_gen_mod)
hos_or <- exp(hos_b1)
hos_or_confint <- exp(hos_confint[2,])
hos_p_confint <- exp(hos_confint)/(1 + exp(hos_confint))
```
  
The estimated odds ratio readmission risk for HOSPITAL is $e^{\hat{B_1}} = e^{0.249} = 1.283$, 95% CI: (1.251, 1.316); these results provide evidence that relative odds of readmission increases between 25.1% - 31.8% for a one value increase HOSPITAL score.  
  
The estimated model for probability of readmission can be estimated as:  

$$p_{HOSP_i} = \frac{e^{-2.794 + 0.242*HOSP_i + 0.292*Male_i}}{1+e^{-2.794 + 0.242*HOSP_i + 0.292*Male_i}}$$  
  
Full model diagnostics are available in [Appendix F](#AppendixF)  
  
```{r hos_gen_rename}
readmit_hos_gen <- readmit_hos_gen %>%
  rename(Gender = Value)
```

```{r hos_modplot}
x <- seq(0, 11, 0.1)

gen <- rep(c("Male", "Female"), each = 111)

y_male <- exp(hos_b0 + hos_b1*x + hos_b2) / (1 + (exp(hos_b0 + hos_b1*x + hos_b2)))
y_female <- exp(hos_b0 + hos_b1*x) / (1 + (exp(hos_b0 + hos_b1*x)))
y <- c(y_male, y_female)

ym_025 <- exp(hos_confint[1,1] + hos_confint[2,1]*x + hos_confint[3,1]) / (1 + (exp(hos_confint[1,1] + hos_confint[2,1]*x + hos_confint[3,1])))
ym_975 <- exp(hos_confint[1,2] + hos_confint[2,2]*x + hos_confint[3,2]) / (1 + (exp(hos_confint[1,2] + hos_confint[2,2]*x + hos_confint[3,2])))

yf_025 <- exp(hos_confint[1,1] + hos_confint[2,1]*x) / (1 + (exp(hos_confint[1,1] + hos_confint[2,1]*x)))
yf_975 <- exp(hos_confint[1,2] + hos_confint[2,2]*x) / (1 + (exp(hos_confint[1,2] + hos_confint[2,2]*x)))

y_025 <- c(ym_025, yf_025)
y_975 <- c(ym_975, yf_975)

two_x <- rep(x, times=2)
hos_modline <- data.frame(HOSPITAL = two_x, Gender = as.factor(gen), 
                           Fit = y, CI_lower = y_025, CI_upper = y_975)

hos_plt <- ggplot(hos_modline, aes(HOSPITAL, Fit)) + 
  geom_line() + 
  geom_line(aes(x=HOSPITAL, y=CI_lower), lty=2) + 
  geom_line(aes(x=HOSPITAL, y=CI_upper), lty=2) + 
  geom_point(data=readmit_hos_gen, aes(x=HOSPITAL, y=p.Readmit), alpha=0.6, size=3) + 
  scale_y_continuous(breaks = seq(0, 0.7, 0.1), limits = c(0, 0.7)) + 
  scale_x_continuous(breaks = seq(0, 11, 2), limits = c(0, 11)) + 
  theme_minimal() + 
  facet_wrap(vars(Gender)) + labs(x = "HOSPITAL Score", y = "Probability of Readmission") + 
  ggtitle(paste("Probability of Readmission by HOSPITAL: \nSample Readmission Rate + Fitted Model"))

suppressWarnings(print(hos_plt))
```
  
  
## Additional Model Fitting  
  
  - Explore patterns within the <30 day readmissions for changes in scores. Model LOS against acuity scores. 
  
  
