# Appendices

## Appendix A: Summary Statistics Tables {#AppendixA}

```{r appendA}
readmit_cci_org %>% 
  kbl(caption = "Readmission Empirical Statistics by CCI Score", digits=3,
      col.names = c("CCI Score", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_classic_2(full_width = F)


readmit_lace_org %>% 
  kbl(caption = "Readmission Empirical Statistics by LACE Score", digits=3,
      col.names = c("LACE Score", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_classic_2(full_width = F)


readmit_hos_org %>% 
  kbl(caption = "Readmission Empirical Statistics by HOSPITAL Score", digits=3,
      col.names = c("HOS Score", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_classic_2(full_width = F)
```
  
## Appendix B: Plots of Empirical Logits by Year, Score {#AppendixB}
```{r appendB}
readmit_yr <- bind_rows(readmit_yr_cci, readmit_yr_lace, readmit_yr_hos) 

readmit_plot <- readmit_yr %>% na_if(-Inf)
ggplot(readmit_plot, aes(x = Value, y = logit.Readmit, shape = Score)) + 
  geom_point(alpha = 0.4, size = 3) + geom_line() + 
  facet_wrap(vars(Year)) + 
  theme_minimal() + 
  labs(x = "Acuity Score", y = "Empirical Logit", shape = "Score") + 
  ggtitle("Empirical Logit by Calculated Score, Year")

yr_cci_plot <- readmit_yr_cci %>% na_if(-Inf)
ggplot(yr_cci_plot, aes(x = Value, y = logit.Readmit, col= as.factor(Year))) + 
  geom_point(alpha = 0.4, size = 3) + geom_line() + 
  theme_minimal() + 
  labs(x = "CCI Score", y = "Empirical Logit", col = "Year") + 
  ggtitle("Empirical Logit by CCI Score, Year")

yr_lace_plot <- readmit_yr_lace %>% na_if(-Inf)
ggplot(yr_lace_plot, aes(x = Value, y = logit.Readmit, col= as.factor(Year))) + 
  geom_point(alpha = 0.4, size = 3) + geom_line() + 
  theme_minimal() + 
  labs(x = "LACE Score", y = "Empirical Logit", col = "Year") + 
  ggtitle("Empirical Logit by LACE Score, Year")

yr_hos_plot <- readmit_yr_hos %>% na_if(-Inf)
ggplot(yr_hos_plot, aes(x = Value, y = logit.Readmit, col= as.factor(Year))) + 
  geom_point(alpha = 0.4, size = 3) + geom_line() + 
  theme_minimal() + 
  labs(x = "HOSP Score", y = "Empirical Logit", col = "Year") + 
  ggtitle("Empirical Logit by HOSPITAL Score, Year")
```
  
## Appendix C: Demographic EDA Tables, Plots {#AppendixC}  
```{r appendc_cci}
readmit_cci_gen %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by CCI Score, Gender", digits=3,
      col.names = c("CCI Score", "Gender", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T)

readmit_cci_re %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by CCI Score, Race/Ethnicity", digits=3,
      col.names = c("CCI Score", "Race/Ethnicity", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T) 

readmit_cci_ins %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by CCI Score, Insurance", digits=3,
      col.names = c("CCI Score", "Insurance", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T) 

cci_gen_plot <- readmit_cci_gen %>% na_if(-Inf)
ggplot(cci_gen_plot, aes(x = CCI, y=logit.Readmit, shape=Value, label=CCI)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) +
  geom_text() + 
  labs(x = "CCI Score", y = "Empirical Logit", shape = "Gender") + 
  theme_minimal() + ggtitle("Empirical Logit by CCI Score, Gender")

cci_re_plot <- readmit_cci_re %>% na_if(-Inf)
ggplot(cci_re_plot, aes(x = CCI, y=logit.Readmit, shape=Value, label=CCI)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) + 
  geom_text() + 
  labs(x = "CCI Score", y = "Empirical Logit", shape = "Race/Ethnicity") + 
  theme_minimal() + ggtitle("Empirical Logit by CCI Score, Race/Ethnicity")

cci_ins_plot <- readmit_cci_ins %>% na_if(-Inf)
ggplot(cci_ins_plot, aes(x = CCI, y=logit.Readmit, shape=Value, label=CCI)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) + 
  geom_text() + 
  labs(x = "CCI Score", y = "Empirical Logit", shape = "Insurance") + 
  theme_minimal() + ggtitle("Empirical Logit by CCI Score, Insurance")
```

```{r appendc_lace}
readmit_lace_gen %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by LACE Score, Gender", digits=3,
      col.names = c("LACE Score", "Gender", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T) 

readmit_lace_re %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by LACE Score, Race/Ethnicity", digits=3,
      col.names = c("LACE Score", "Race/Ethnicity", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T) 

readmit_lace_ins %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by LACE Score, Insurance", digits=3,
      col.names = c("LACE Score", "Insurance", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T) 


lace_gen_plot <- readmit_lace_gen %>% na_if(-Inf)
ggplot(lace_gen_plot, aes(x = LACE, y=logit.Readmit, shape=Gender, label=LACE)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) +
  geom_text() + 
  labs(x = "LACE Score", y = "Empirical Logit", shape = "Gender") + 
  theme_minimal() + ggtitle("Empirical Logit by LACE Score, Gender")

lace_re_plot <- readmit_lace_re %>% na_if(-Inf)
ggplot(lace_re_plot, aes(x = LACE, y=logit.Readmit, shape=Value, label=LACE)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) + 
  geom_text() + 
  labs(x = "LACE Score", y = "Empirical Logit", shape = "Race/Ethnicity") + 
  theme_minimal() + ggtitle("Empirical Logit by LACE Score, Race/Ethnicity")

lace_ins_plot <- readmit_lace_ins %>% na_if(-Inf)
ggplot(lace_ins_plot, aes(x = LACE, y=logit.Readmit, shape=Value, label=LACE)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) + 
  geom_text() + 
  labs(x = "LACE Score", y = "Empirical Logit", shape = "Insurance") + 
  theme_minimal() + ggtitle("Empirical Logit by LACE Score, Insurance")
```


```{r appendc_hos}
readmit_hos_gen %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by HOSPITAL Score, Gender", digits=3,
      col.names = c("HOSP Score", "Gender", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T) 

readmit_hos_re %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by HOSPITAL Score, Race/Ethnicity", digits=3,
      col.names = c("HOSP Score", "Race/Ethnicity", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T) 

readmit_hos_ins %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by HOSPITAL Score, Insurance", digits=3,
      col.names = c("HOSP Score", "Insurance", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T)

hos_gen_plot <- readmit_hos_gen %>% na_if(-Inf)
ggplot(hos_gen_plot, aes(x = HOSPITAL, y=logit.Readmit, shape=Gender, label=HOSPITAL)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) +
  geom_text() + 
  labs(x = "HOSP Score", y = "Empirical Logit", shape = "Gender") + 
  theme_minimal() + ggtitle("Empirical Logit by HOSPITAL Score, Gender")

hos_re_plot <- readmit_hos_re %>% na_if(-Inf)
ggplot(hos_re_plot, aes(x = HOSPITAL, y=logit.Readmit, shape=Value, label=HOSPITAL)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) + 
  geom_text() + 
  labs(x = "HOSP Score", y = "Empirical Logit", shape = "Race/Ethnicity") + 
  theme_minimal() + ggtitle("Empirical Logit by HOSPITAL Score, Race/Ethnicity")

hos_ins_plot <- readmit_hos_ins %>% na_if(-Inf)
ggplot(hos_ins_plot, aes(x = HOSPITAL, y=logit.Readmit, shape=Value, label=HOSPITAL)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) + 
  geom_text() + 
  labs(x = "HOSP Score", y = "Empirical Logit", shape = "Insurance") + 
  theme_minimal() + ggtitle("Empirical Logit by HOSPITAL Score, Insurance")
```


## Appendix D: CCI Model Comparison and Diagnostics {#AppendixD}
Since the base CCI model showed no evidence of a relationship between readmission risk and CCI score, expanded covariate models were not considered.  

```{r cci_diag}
CCI_eq <- "$B_0 + B_1*CCI$"
CCI_est <- round(CCI_mod0$coefficients[2], 3)
CCI_confint <- paste(round(cci_confint[2,1], 3), 
                     round(cci_confint[2,2], 3), sep = ", ")
CCI_dev <- round(CCI_mod0$deviance)
CCI_df <- CCI_mod0$df.residual
CCI_aic <- round(AIC(CCI_mod0))

cci_mod_tab <- data.frame(cbind(CCI_eq, 
                                CCI_est, 
                                CCI_confint,
                                CCI_dev, 
                                CCI_df, 
                                CCI_aic))
colnames(cci_mod_tab) <- c("$log(\\frac{p_{CCI_i}}{1-p_{CCI_{i}}})$",
                           "$B_1$ Estimate", "$B_1$ 95% CI",
                           "Residual Deviance", "Degrees of Freedom",
                           "AIC")
rownames(cci_mod_tab) <- NULL

cci_models <- kbl(cci_mod_tab, caption = "CCI Model Summary", escape = FALSE) %>%
  kable_classic_2(full_width = FALSE)
cci_models
```


  
## Appendix E: LACE Model Comparisons {#AppendixE}

```{r lace_models}
lace_eq <- c("$B_0 + B_1*LACE$", "$B_0 + B_1*LACE + B_2*Gender$",
             "$B_0 + B_1*LACE + B_2*Age + \\\\ \\ \\ \\ \\  B_3*Year + B_4*Gender + B5*Insurance$",
             "$B_0 + B_1*LACE * B_2*Age * \\\\  \\ \\ \\ \\ B_3*Year * B_4*Gender * B5*Insurance$")
lace_est <- c(round(lace_mod0$coefficients[2], 3),
              round(lace_gen_mod$coefficients[2], 3),
              round(lace_add_mod$coefficients[2], 3),
              round(lace_sat_mod$coefficients[2], 3))
lace_mod0_confint <- round(confint(lace_mod0)[2,], 3)
lace_gen_confint <- round(confint(lace_gen_mod)[2,], 3)
lace_add_confint <- round(confint(lace_add_mod)[2,], 3)
lace_sat_confint <- round(confint(lace_sat_mod)[2,], 3)
lace_ci <- c(paste(lace_mod0_confint[1], lace_mod0_confint[2], sep = ", "),
             paste(lace_gen_confint[1], lace_gen_confint[2], sep = ", "),
             paste(lace_add_confint[1], lace_add_confint[2], sep = ", "),
             paste(lace_sat_confint[1], lace_sat_confint[2], sep = ", "))
lace_dev <- c(round(lace_mod0$deviance), round(lace_gen_mod$deviance),
              round(lace_add_mod$deviance), round(lace_sat_mod$deviance))
lace_df <- c(round(lace_mod0$df.residual), round(lace_gen_mod$df.residual),
              round(lace_add_mod$df.residual), round(lace_sat_mod$df.residual))
lace_aic <- c(round(AIC(lace_mod0)), round(AIC(lace_gen_mod)),
              round(AIC(lace_add_mod)), round(AIC(lace_sat_mod)))

lace_mod_tab <- data.frame(cbind(lace_eq, lace_est, lace_ci, 
                                 lace_dev, lace_df, lace_aic))
colnames(lace_mod_tab) <- c("$log(\\frac{p_{LACE_i}}{1-p_{LACE_{i}}})$",
                           "$B_1$ Estimate", "$B_1$ 95% CI",
                           "Residual Deviance", "Degrees of Freedom",
                           "AIC")
rownames(lace_mod_tab) <- NULL

lace_models <- kbl(lace_mod_tab, caption = "LACE Model Comparison", 
                   linesep = "\\addlinespace", escape = FALSE) %>%
  kable_classic_2(full_width = FALSE)

lace_models

```
  
## Appendix F: HOSPITAL Model Comparisons {#AppendixF}  
```{r stayduration_models}
hos_eq <- c("$B_0 + B_1*HOSPITAL$", "$B_0 + B_1*HOSPITAL + B_2*Gender$",
             "$B_0 + B_1*HOSPITAL + B_2*Age + \\\\ \\ \\ \\ \\  B_3*Year + B_4*Gender + B5*Insurance$",
             "$B_0 + B_1*HOSPITAL * B_2*Age * \\\\ \\ \\ \\ \\  B_3*Year * B_4*Gender * B5*Insurance$")
hos_est <- c(round(hos_mod0$coefficients[2], 3),
              round(hos_gen_mod$coefficients[2], 3),
              round(hos_add_mod$coefficients[2], 3),
              round(hos_sat_mod$coefficients[2], 3))
hos_mod0_confint <- round(confint(hos_mod0)[2,], 3)
hos_gen_confint <- round(confint(hos_gen_mod)[2,], 3)
hos_add_confint <- round(confint(hos_add_mod)[2,], 3)
hos_sat_confint <- round(confint(hos_sat_mod)[2,], 3)
hos_ci <- c(paste(hos_mod0_confint[1], hos_mod0_confint[2], sep = ", "),
             paste(hos_gen_confint[1], hos_gen_confint[2], sep = ", "),
             paste(hos_add_confint[1], hos_add_confint[2], sep = ", "),
             paste(hos_sat_confint[1], hos_sat_confint[2], sep = ", "))
hos_dev <- c(round(hos_mod0$deviance), round(hos_gen_mod$deviance),
              round(hos_add_mod$deviance), round(hos_sat_mod$deviance))
hos_df <- c(round(hos_mod0$df.residual), round(hos_gen_mod$df.residual),
              round(hos_add_mod$df.residual), round(hos_sat_mod$df.residual))
hos_aic <- c(round(AIC(hos_mod0)), round(AIC(hos_gen_mod)),
              round(AIC(hos_add_mod)), round(AIC(hos_sat_mod)))

hos_mod_tab <- data.frame(cbind(hos_eq, hos_est, hos_ci, hos_dev, hos_df, hos_aic))
colnames(hos_mod_tab) <- c("$log(\\frac{p_{HOSPITAL_i}}{1-p_{HOSPITAL_{i}}})$",
                           "$B_1$ Estimate", "$B_1$ 95% CI",
                           "Residual Deviance", "Degrees of Freedom",
                           "AIC")
rownames(hos_mod_tab) <- NULL

hos_models <- kbl(hos_mod_tab, caption = "HOSPITAL Model Comparison", 
                   linesep = "\\addlinespace", escape = FALSE) %>%
  kable_classic_2(full_width = FALSE)

hos_models

```

## Appendix G: LOS Follow Up Analysis {#AppendixG}

```{r filter_readmits}
snf_readmits <- snf_data_fit %>% filter(Readmit == "Y")
```

```{r los_plots}
los_cci_plot <- snf_readmits %>%
  group_by(CCI, Gender) %>%
  summarize(mean.stay = mean(StayDurationDays))

ggplot(los_cci_plot, aes(x = CCI, y = mean.stay, lty = Gender)) + 
  geom_line() + 
  theme_minimal() + 
  scale_x_continuous(breaks = seq(0, 14, 2), limits = c(0, 14)) + 
  scale_y_continuous(breaks = seq(0, 16, 2), limits = c(0, 16)) +
  labs(y = "Average LOS") + 
  ggtitle("Average Length of Stay by CCI Score, Gender")

los_lace_plot <- snf_readmits %>%
  group_by(LACE, Gender) %>%
  summarize(mean.stay = mean(StayDurationDays))

ggplot(los_lace_plot, aes(x = LACE, y = mean.stay, lty = Gender)) + 
  geom_line() + 
  theme_minimal() + 
  scale_x_continuous(breaks = seq(4, 18, 2), limits = c(4, 18)) + 
  scale_y_continuous(breaks = seq(0, 16, 2), limits = c(0, 16)) +
  labs(y = "Average LOS") + 
  ggtitle("Average Length of Stay by LACE Score, Gender")

los_hos_plot <- snf_readmits %>%
  group_by(HOSPITAL, Gender) %>%
  summarize(mean.stay = mean(StayDurationDays))

ggplot(los_hos_plot, aes(x = HOSPITAL, y = mean.stay, lty = Gender)) + 
  geom_line() + 
  theme_minimal() + 
  scale_x_continuous(breaks = seq(0, 11, 2), limits = c(0, 11)) +
  scale_y_continuous(breaks = seq(0, 16, 2), limits = c(0, 16)) +
  labs(y = "Average LOS") + 
  ggtitle("Average Length of Stay by HOSPITAL Score, Gender")
```

```{r los_mods}
# Linear Models
cci_los_mod <- lm(StayDurationDays ~ CCI, data = snf_data_fit)
lace_los_mod <- lm(StayDurationDays ~ LACE + Gender, data = snf_data_fit)
hos_los_mod <- lm(StayDurationDays ~ HOSPITAL + Gender, data = snf_data_fit)

# Pearson's correlation coef
cors <- c(round(cor(snf_data_fit$CCI, snf_data_fit$StayDurationDays), 3),
          round(cor(snf_data_fit$LACE, snf_data_fit$StayDurationDays), 3),
          round(cor(snf_data_fit$HOSPITAL, snf_data_fit$StayDurationDays), 3))

los_ests <- c(round(cci_los_mod$coefficients[2], 3),
              round(lace_los_mod$coefficients[2], 3),
              round(hos_los_mod$coefficients[2], 3))

los_ci <- c(paste(round(confint(cci_los_mod)[2,1], 3), 
                  round(confint(cci_los_mod)[2,2], 3), sep = ", "),
             paste(round(confint(lace_los_mod)[2,1], 3), 
                   round(confint(lace_los_mod)[2,2], 3), sep = ", "),
             paste(round(confint(hos_los_mod)[2,1], 3), 
                   round(confint(hos_los_mod)[2,2], 3), sep = ", "))

score <- c("CCI", "LACE", "HOSPITAL")

los_tab <- data.frame(cbind(score, cors, los_ests, los_ci))
colnames(los_tab) <- c("Score", "Pearson's Corr", "LM Est", "95% CI")

los_models <- kbl(los_tab, caption = "Length of Stay by Score", 
                   linesep = "\\addlinespace", escape = FALSE) %>%
  kable_classic_2(full_width = FALSE)

los_models

```

