---
title: "Readmission Analysis"
author: "Amira Burns"
date: "2023-01-24"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# -- Load Libraries
library(readxl) # read in Excel files
library(car) # Type III Sums of Squares Anova
library(emmeans)  # multiple comparisons
library(tidyverse) # data processing, visualization
library(lubridate) # process dates
library(ggsci) # colors
library(rstatix)
library(gridExtra) # make and arrange tables
library(gtable) 
library(kableExtra)
library(DescTools) # categorical correlation
library(nnet) # multinomial model fitting
library(lme4) # mixed-level model fitting
library(corrr) # tidy correlations
```

```{r load}
snf_data <- read_xlsx("/data/SNF_CODED_CALCULATED_SCORES_04042022.xlsx",
                      sheet = "CODED DATA AND CALCULATIONS")

readmits <- read_xlsx("/data/Stern 30-day Readmissions 2014 - 2019.xlsx")
```

```{r format_vars}
snf_data <- snf_data %>%
  transmute(SternClientID = `Stern Client Id`,
            MRN = MRN,
            Year = WorkSheet,
            CurrentAdmit = as.Date(`Current Admit`, format = "%m/%d/%y"),          
            DischargeDate = as.Date(`Discharge Date`, format = "%m/%d/%y"),
            Gender = factor(Gender),
            Race = Race,
            Ethnicity = factor(Ethnicity),
            InsurancePlanName = (InsurancePlanName),
            ED6moPrior = factor(`LACE Num_of_ED_visits_prior 6months`),
            PatientAge = PatientAge,
            AdmissionHospital = factor(AdmissionHospital),
            CCIAgeScore = ordered(`CCI AGE SCORE`),
            LACELOSDaysScore = ordered(`LACE LOSDays SCORE`),
            LOSDays = LOSDays,
            LOS5Days = factor(`LOS>=5days`),
            HOSPITALLOS5Days = factor(`HOSPITAL LOS>=5days`),
            VisitType = factor(VisitType),
            AdmitDtm = as.Date(AdmitDtm, format = "%m/%d/%y"),
            DischargeDtm = as.Date(DischargeDtm, format = "%m/%d/%y"),
            NumAdmitPastYear = `NumberOfAdmissionInPastYear`,
            PriorAdmin = ordered(`HOSPITAL # OF admission prior yr`),
            Cancer = factor(`HOSPITAL SCORE D/C ONC SERVICE`),
            AcuteAdmin = factor(`LACE ACUTE ADMISSION`),
            AdminType = factor(`HOSPITAL SCORE INDEX ADMISSION TYPE`),
            Hemoglobin = `Hemoglobin at discharge`,
            HemoglobinLevel = factor(`HOSPITAL SCORE Hemoglobin at discharge`),
            Sodium = `Sodium, Serum at discharge`,
            SodiumLevel = factor(`HOSPITAL SCORE Sodium`),
            LACECCI = `LACE CCI SCORE`,
            MyoInfarc = factor(`Myocardial infarction`),
            CongHrtFail = factor(`Congestive heart failure`),
            PeriphVascDis = factor(`Peripheral vascular disease`),
            CerebroVascDis = factor(`Cerebrovascular disease`),
            Dementia = factor(Dementia),
            ChronPulmoDis = factor(`Chronic pulmonary disease`),
            RheuConTisDis = factor(`Rheumatic disease=connective tissue disease`),
            PepUlcDis = factor(`Peptic ulcer disease`),
            MildLiverDis = factor(`MILD liver disease`), # combine into one liver disease var
            ModSevLiverDis = factor(`MODERATE or SEVERE  liver disease`),
            DiabetesWOChrCom = factor(`Diabetes WITHOUT chronic complication`), # combine into one diabetes var
            DiabetesWChrCom = factor(`Diabetes WITH chronic complication`),
            HemiParaPlegia = factor(`Hemiplegia or paraplegia`),
            RenalDisCKD = factor(`Renal disease = mod to severe CKD`),
            Malignancy = factor(`Any Malignancy`),
            MetaSolidTumor = factor(`Metastatic solid tumour`),
            AidsHIV = factor(`AIDS/HIV`),
            CCI = `CALCULATED CCI SCORE`,
            LACE = `CALCULATED LACE SCORE`,
            HOSPITAL = `CALCULATED HOSPITAL SCORE`,
            Readmit30 = `READMISSION <30DAYS`) %>%
  mutate(StayDurationDays = as.numeric((DischargeDate - CurrentAdmit)),
         DtmDuration = DischargeDtm - AdmitDtm)
```  

  
```{r standardize}
# Exclude records before 2014 due to reporting changes
snf_data <- snf_data %>% filter(Year > 2013)

# Create new column for whether or not record is a readmission
snf_data <- snf_data %>%
  mutate(Readmit30 = ifelse(Readmit30 == "N/A", "O", Readmit30)) %>%
  rename(Readmit = Readmit30)


# Standardize values of Race, Insurance, Liver Disease, Diabetes
snf_data <- snf_data %>%
  mutate(Race = as.factor(ifelse(Race == "White", "Caucasian/White",
                       ifelse((Race == "Declined" | Race == "Not Specified" | Race == "Unknown"), "Unavailable/Unknown",
                              ifelse(Race == "Multiracial", "Other/Multiracial", Race)))),
         InsurancePlanCleaned = ifelse(grepl("MEDICARE", InsurancePlanName), "MCARE_MCAID",
                                       ifelse(grepl("MCARE", InsurancePlanName), "MCARE_MCAID",
                                              ifelse(grepl("MEDICAID", InsurancePlanName), "MCARE_MCAID",
                                                     ifelse(grepl("MCAID", InsurancePlanName), "MCARE_MCAID",
                                                            "NO_MCARE_MCAID")))),
         LiverDis = ordered(ifelse(ModSevLiverDis == 3, 3,
                                   ifelse(MildLiverDis == 1, 1, 0))),
         Diabetes = ordered(ifelse(DiabetesWChrCom == 2, 2,
                                   ifelse(DiabetesWOChrCom == 1, 1, 0))))

# relevel Readmit factor, combine original admissions with readmissions > 30 days
snf_data <- snf_data %>%
  mutate(Readmit = ifelse(Readmit == "O", "N", Readmit)) %>%
  mutate(Readmit = as.factor(Readmit))

```

```{r, nas}
# Summarize missing values by variable
nas <- map(snf_data, ~sum(is.na(.)))
# nas %>% as_tibble(nas) 

# Look at records with missing values
NAlook <- function(x) rowSums(x) > 0 
NAs <- snf_data %>% filter(NAlook( across( .cols = everything(), .fns = ~ is.na(.x))))

# remove small number of records with NA values
snf_data <- snf_data %>% na.omit()
```  

```{r data_prep}
# Aggregate Race/Ethnicity
snf_data <- snf_data %>%
  mutate(Race_Eth = factor(ifelse(Ethnicity == "Hispanic or Latino", "Hispanic/Latino", as.character(Race))))

snf_data_a <- snf_data %>% 
  filter(Gender != "Unspecified") %>%
  mutate(Race_Eth = fct_recode(Race_Eth, "Other/Multiracial" = "Native Amer/Alaskan"),
         Insurance = as.factor(InsurancePlanCleaned))
snf_data_a$Gender <- droplevels(snf_data_a$Gender)



```

```{r join_los}
# join length of stay in snf for readmissions 3to main data
readmits <- readmits %>%
  mutate(SternClientID = as.numeric(`Stern ID #`)) %>%
  rename(LOS_snf = LOS) %>%
  select(c(SternClientID, LOS_snf))

snf_data <- snf_data_a %>%
  left_join(readmits, by = "SternClientID")

```

## Introduction  

  - **Research Question**: Are higher acuity scores associated with greater probability of readmission to hospital from skilled nursing facility within 30 days of initial discharge? Acuity scores considered in this analysis are common clinical scores: CCI, LACE, HOSPITAL.
  - **Alternative Hypothesis** $H_a$: Higher acuity scores are associated with higher probability of readmission.  
  - **Null Hypothesis** $H_0$: Higher acuity scores are not associated with higher probability of readmission.  
  - **Response variable**: binary Y/N if a record was for a readmission to an inpatient facility within 30 days of previous discharge. Three possible values are Original admission, Readmission outside 30 days, and Readmission within 30 days. Because financial penalties are assessed on readmissions within 30 days, the first two categories were combined into a **N** category.  
  - **Observational units**: primary observational variables of interest are the three calculated scores assigned to individuals at each admission. Covariates of interest are:  
    - Year: study period 2014-2019
    - Gender: Male/Female  
    - Race/Ethnicity: groups in the dataset are African American/Black, Asian, Caucasian/White, Hispanic/Latino, Other/Multiracial, and Unavailable/Unknown. Sample sizes were too small for some of these groups for us to include it in this analysis, but we note its association with each of the calculated scores and hvae interest in studying this topic further.  
    - Insurance: Medicare-Medicaid/No Medicare-Medicaid as an indicator of socioeconomic status.  
  
## Methods  
Analyses will be conducted in R. All observations from 2010-2013 were removed from analysis due to changes in reporting calculated scores. An additional 33 records with missing values were excluded from overall analysis. Summary statistics for each calculated score will be reviewed, including: number of readmissions, readmission rate, odds of readmission, and log odds. Covariates will be reviewed for sufficient sample size within each group to include in model-fitting. Exploratory data analysis will also include visualizations of empirical log odds (logits) for each calculated score across all potential covariates.  
Model fitting will begin with logistic regression considering the association of acuity score with readmission risk. Separate models will be fitted for each acuity score, and expand to consider covariates as appropriate. Additional observations may be dropped or aggregated in consideration of sample size and will be noted in each case. Individual models will be assessed through reviewing deviance residuals and conducting a $\chi^2$ goodness-of-fit test. Individual predictors will be assessed with confidence intervals. Models will be compared using Akaike's Information Criteria.  
  
*Note: add a MC simulation if there's enough time!*  


## Exploratory Data Analysis

Our primary research interest is whether or not the probability of readmission is associated with calculated score. We calculate the odds $\frac{p}{1-p}$ empirical log odds $log(\frac{p}{1-p})$ of readmissions associated with each level of each acuity score and visualize the potential associations, where $p$ is the probability that a record is of a readmission within 30 days. Summary tables for CCI, LACE, and HOSPITAL can be found in [Appendix A](#AppendixA): .

```{r readmit_CCI}
readmit_cci <- snf_data_a %>%
  group_by(CCI) %>%
  summarize(meanAge = mean(PatientAge), n=n(), 
            n.Readmit = sum(Readmit == "Y"),
            p.Readmit = sum(Readmit == "Y")/n,
            odds.Readmit = p.Readmit / (1 - p.Readmit),
            logit.Readmit = log(odds.Readmit))
```

```{r readmit_LACE}
readmit_lace <- snf_data_a %>%
  group_by(LACE) %>%
  summarize(meanAge = mean(PatientAge), n=n(), 
            n.Readmit = sum(Readmit == "Y"),
            p.Readmit = sum(Readmit == "Y")/n,
            odds.Readmit = p.Readmit / (1 - p.Readmit),
            logit.Readmit = log(odds.Readmit))
```

```{r readmit_HOS}
readmit_hos <- snf_data_a %>%
  group_by(HOSPITAL) %>%
  summarize(meanAge = mean(PatientAge), n=n(), 
            n.Readmit = sum(Readmit == "Y"),
            p.Readmit = sum(Readmit == "Y")/n,
            odds.Readmit = p.Readmit / (1 - p.Readmit),
            logit.Readmit = log(odds.Readmit))

```

```{r readmit_scores_plot}
# combine dfs together
cci_bind <- readmit_cci %>%
  mutate(Score = rep("CCI")) %>%
  rename(Value = CCI) %>%
  relocate(Score)

lace_bind <- readmit_lace %>%
  mutate(Score = rep("LACE")) %>%
  rename(Value = LACE) %>%
  relocate(Score)

hos_bind <- readmit_hos %>%
  mutate(Score = rep("HOSPITAL")) %>%
  rename(Value = HOSPITAL) %>%
  relocate(Score)

readmit_data <- bind_rows(cci_bind, lace_bind, hos_bind)

# remove -inf rows for plotting
readmit_plot <- readmit_data %>% na_if(-Inf)

# plot empirical logits 
ggplot(readmit_plot, aes(x = Value, y = logit.Readmit, shape = Score, label = Value)) + 
  geom_point(alpha=0.4, size = 3) + 
  geom_text() +  geom_line(alpha=0.3) + 
  theme_minimal() + 
  labs(x = "Acuity Score", y = "Empirical Logit") + 
  facet_wrap(vars(Score)) + 
  ggtitle("Empirical Logits by Acuity Score")
```
A linear association between CCI score and empirical logit is not clear, especially considering score values greater than 8. A linear association between HOSPITAL score and empirical logit is quite pronounced; while the linear association between LACE score and empirical logit is also quite strong, we can observe two potential outliers for LACE score values of 3 and 18.  
  
We also want to consider whether or not probability of readmission changes over time, with respect to acuity score. Various plots examining readmission by score over year can be found in [Appendix B](#AppendixB); no interaction between score and year is apparent.  
```{r readmit_yr}
readmit_yr_cci <- snf_data_a %>%
  group_by(CCI, Year) %>%
  rename(Value = CCI) %>%
  summarize(meanAge = mean(PatientAge), n=n(), 
            n.Readmit = sum(Readmit == "Y"),
            p.Readmit = sum(Readmit == "Y")/n,
            odds.Readmit = p.Readmit / (1 - p.Readmit),
            logit.Readmit = log(odds.Readmit)) %>%
  mutate(Score = rep("CCI"))

readmit_yr_lace <- snf_data_a %>%
  group_by(LACE, Year) %>%
  rename(Value = LACE) %>%
  summarize(meanAge = mean(PatientAge), n=n(), 
            n.Readmit = sum(Readmit == "Y"),
            p.Readmit = sum(Readmit == "Y")/n,
            odds.Readmit = p.Readmit / (1 - p.Readmit),
            logit.Readmit = log(odds.Readmit)) %>%
  mutate(Score = rep("LACE"))

readmit_yr_hos <- snf_data_a %>%
  group_by(HOSPITAL, Year) %>%
  rename(Value = HOSPITAL) %>%
  summarize(meanAge = mean(PatientAge), n=n(), 
            n.Readmit = sum(Readmit == "Y"),
            p.Readmit = sum(Readmit == "Y")/n,
            odds.Readmit = p.Readmit / (1 - p.Readmit),
            logit.Readmit = log(odds.Readmit)) %>%
  mutate(Score = rep("HOSPITAL"))

```


We are also interested in the potential effect demographic factors have on the relationship between readmission rate and acuity score. Due to the small sample sizes from considering multiple demographics together, we will disaggregate readmission by each acuity score over one demographic factor (Gender, Race/Ethnicity, Insurance) at a time. Tables and plots for readmission logits by demographic covariates are available in [Appendix C](#AppendixC)  

```{r readmit_cci_demo}
readmit_cci_gen <- snf_data_a %>%
  group_by(CCI, Gender) %>%
  rename(Value = Gender) %>%
  summarize(meanAge = mean(PatientAge), n=n(), 
            n.Readmit = sum(Readmit == "Y"),
            p.Readmit = sum(Readmit == "Y")/n,
            odds.Readmit = p.Readmit / (1 - p.Readmit),
            logit.Readmit = log(odds.Readmit)) %>%
  mutate(Demo = rep("Gender"))

readmit_cci_re <- snf_data_a %>%
  group_by(CCI, Race_Eth) %>%
  rename(Value = Race_Eth) %>% 
  summarize(meanAge = mean(PatientAge), n=n(), 
            n.Readmit = sum(Readmit == "Y"),
            p.Readmit = sum(Readmit == "Y")/n,
            odds.Readmit = p.Readmit / (1 - p.Readmit),
            logit.Readmit = log(odds.Readmit)) %>%
  mutate(Demo = rep("Race/Ethnicity"))

readmit_cci_ins <- snf_data_a %>%
  group_by(CCI, Insurance) %>%
  rename(Value = Insurance) %>%
  summarize(meanAge = mean(PatientAge), n=n(), 
            n.Readmit = sum(Readmit == "Y"),
            p.Readmit = sum(Readmit == "Y")/n,
            odds.Readmit = p.Readmit / (1 - p.Readmit),
            logit.Readmit = log(odds.Readmit)) %>%
  mutate(Demo = rep("Insurance"))

```

```{r readmit_lace_demo}
readmit_lace_gen <- snf_data_a %>%
  group_by(LACE, Gender) %>%
  rename(Value = Gender) %>%
  summarize(meanAge = mean(PatientAge), n=n(), 
            n.Readmit = sum(Readmit == "Y"),
            p.Readmit = sum(Readmit == "Y")/n,
            odds.Readmit = p.Readmit / (1 - p.Readmit),
            logit.Readmit = log(odds.Readmit)) %>%
  mutate(Demo = rep("Gender"))

readmit_lace_re <- snf_data_a %>%
  group_by(LACE, Race_Eth) %>%
  rename(Value = Race_Eth) %>% 
  summarize(meanAge = mean(PatientAge), n=n(), 
            n.Readmit = sum(Readmit == "Y"),
            p.Readmit = sum(Readmit == "Y")/n,
            odds.Readmit = p.Readmit / (1 - p.Readmit),
            logit.Readmit = log(odds.Readmit)) %>%
  mutate(Demo = rep("Race/Ethnicity"))

readmit_lace_ins <- snf_data_a %>%
  group_by(LACE, Insurance) %>%
  rename(Value = Insurance) %>%
  summarize(meanAge = mean(PatientAge), n=n(), 
            n.Readmit = sum(Readmit == "Y"),
            p.Readmit = sum(Readmit == "Y")/n,
            odds.Readmit = p.Readmit / (1 - p.Readmit),
            logit.Readmit = log(odds.Readmit)) %>%
  mutate(Demo = rep("Insurance"))
readmit_lace_ins %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by LACE Score, Insurance", digits=3,
      col.names = c("LACE Score", "Insurance", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T) %>%
  collapse_rows(columns=0:1, valign="top")

lace_gen_plot <- readmit_lace_gen %>% na_if(-Inf)
ggplot(lace_gen_plot, aes(x = LACE, y=logit.Readmit, shape=Value, label=LACE)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) +
  geom_text() + 
  labs(x = "LACE Score", y = "Empirical Logit", shape = "Gender") + 
  theme_minimal() + ggtitle("Empirical Logit by LACE Score, Gender")

lace_re_plot <- readmit_lace_re %>% na_if(-Inf)
ggplot(lace_re_plot, aes(x = LACE, y=logit.Readmit, shape=Value, label=LACE)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) + 
  geom_text() + 
  labs(x = "LACE Score", y = "Empirical Logit", shape = "Race/Ethnicity") + 
  theme_minimal() + ggtitle("Empirical Logit by LACE Score, Race/Ethnicity")

lace_ins_plot <- readmit_lace_ins %>% na_if(-Inf)
ggplot(lace_ins_plot, aes(x = LACE, y=logit.Readmit, shape=Value, label=LACE)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) + 
  geom_text() + 
  labs(x = "LACE Score", y = "Empirical Logit", shape = "Insurance") + 
  theme_minimal() + ggtitle("Empirical Logit by LACE Score, Insurance")
  
```
  
  
```{r readmit_hos_demo}
readmit_hos_gen <- snf_data_a %>%
  group_by(HOSPITAL, Gender) %>%
  rename(Value = Gender) %>%
  summarize(meanAge = mean(PatientAge), n=n(), 
            n.Readmit = sum(Readmit == "Y"),
            p.Readmit = sum(Readmit == "Y")/n,
            odds.Readmit = p.Readmit / (1 - p.Readmit),
            logit.Readmit = log(odds.Readmit)) %>%
  mutate(Demo = rep("Gender"))
readmit_hos_gen %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by HOSPITAL Score, Gender", digits=3,
      col.names = c("HOSP Score", "Gender", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T) %>%
  collapse_rows(columns=0:1, valign="top")

readmit_hos_re <- snf_data_a %>%
  group_by(HOSPITAL, Race_Eth) %>%
  rename(Value = Race_Eth) %>% 
  summarize(meanAge = mean(PatientAge), n=n(), 
            n.Readmit = sum(Readmit == "Y"),
            p.Readmit = sum(Readmit == "Y")/n,
            odds.Readmit = p.Readmit / (1 - p.Readmit),
            logit.Readmit = log(odds.Readmit)) %>%
  mutate(Demo = rep("Race/Ethnicity"))
readmit_hos_re %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by HOSPITAL Score, Race/Ethnicity", digits=3,
      col.names = c("HOSP Score", "Race/Ethnicity", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T) %>%
  collapse_rows(columns=0:1, valign="top")

readmit_hos_ins <- snf_data_a %>%
  group_by(HOSPITAL, Insurance) %>%
  rename(Value = Insurance) %>%
  summarize(meanAge = mean(PatientAge), n=n(), 
            n.Readmit = sum(Readmit == "Y"),
            p.Readmit = sum(Readmit == "Y")/n,
            odds.Readmit = p.Readmit / (1 - p.Readmit),
            logit.Readmit = log(odds.Readmit)) %>%
  mutate(Demo = rep("Insurance"))
readmit_hos_ins %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by HOSPITAL Score, Insurance", digits=3,
      col.names = c("HOSP Score", "Insurance", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T) %>%
  collapse_rows(columns=0:1, valign="top")

hos_gen_plot <- readmit_hos_gen %>% na_if(-Inf)
ggplot(hos_gen_plot, aes(x = HOSPITAL, y=logit.Readmit, shape=Value, label=HOSPITAL)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) +
  geom_text() + 
  labs(x = "HOSP Score", y = "Empirical Logit", shape = "Gender") + 
  theme_minimal() + ggtitle("Empirical Logit by HOSPITAL Score, Gender")

hos_re_plot <- readmit_hos_re %>% na_if(-Inf)
ggplot(hos_re_plot, aes(x = HOSPITAL, y=logit.Readmit, shape=Value, label=HOSPITAL)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) + 
  geom_text() + 
  labs(x = "HOSP Score", y = "Empirical Logit", shape = "Race/Ethnicity") + 
  theme_minimal() + ggtitle("Empirical Logit by HOSPITAL Score, Race/Ethnicity")

hos_ins_plot <- readmit_hos_ins %>% na_if(-Inf)
ggplot(hos_ins_plot, aes(x = HOSPITAL, y=logit.Readmit, shape=Value, label=HOSPITAL)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) + 
  geom_text() + 
  labs(x = "HOSP Score", y = "Empirical Logit", shape = "Insurance") + 
  theme_minimal() + ggtitle("Empirical Logit by HOSPITAL Score, Insurance")
```  
  
  
Sample sizes are too small among Race_Ethnicity groups to consider this covariate in model fitting. 


## Model Fitting

Binomial logistic regression is the appropriate model class for our analysis. We start model fitting with a basic model for each calculated score, where the probability that a record is a readmission within 30 days can be modeled as:  


$$
\begin{aligned}
log(\frac{p_{X_{ij}}}{1-p_{X_{ij}}}) &= \beta_0 + \beta_1  X_{ij} \\
p_{X_{ij}} &= \frac{e^{\beta_0 + \beta_1X_{ij}}}{1 + e^{\beta_0 + \beta_1X_{ij}}}
\end{aligned}
$$


where $X_{ij}$ is the $j_{th}$ value of the $i_{th}$ score:  
 + i = {CCI, LACE, HOSPITAL}  
 + j = 0, 1, 2, ..., j
  
```{r models_base}
CCI_mod0 <- glm(cbind(n.Readmit, n-n.Readmit) ~ CCI, family = binomial(link="logit"), data = readmit_cci)
LACE_mod0 <- glm(cbind(n.Readmit, n-n.Readmit) ~ LACE, family = binomial(link="logit"), data = readmit_lace)
HOS_mod0 <- glm(cbind(n.Readmit, n-n.Readmit) ~ HOSPITAL, family = binomial(link="logit"), data = readmit_hos)
```  

Full model diagnostics follow appear in ... 

***

## Appendices

### Appendix A: Summary Statistics Tables (#AppendixA)
```{r appendA}
readmit_cci %>% 
  kbl(caption = "Readmission Empirical Statistics by CCI Score", digits=3,
      col.names = c("CCI Score", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_classic_2(full_width = F)


readmit_lace %>% 
  kbl(caption = "Readmission Empirical Statistics by LACE Score", digits=3,
      col.names = c("LACE Score", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_classic_2(full_width = F)


readmit_hos %>% 
  kbl(caption = "Readmission Empirical Statistics by HOSPITAL Score", digits=3,
      col.names = c("HOS Score", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_classic_2(full_width = F)
```
  
### Appendix B: Plots of Empirical Logits by Year, Score (#AppendixB)  
```{r appendB}
readmit_yr <- bind_rows(readmit_yr_cci, readmit_yr_lace, readmit_yr_hos) 

readmit_plot <- readmit_yr %>% na_if(-Inf)
ggplot(readmit_plot, aes(x = Value, y = logit.Readmit, shape = Score)) + 
  geom_point(alpha = 0.4, size = 3) + geom_line() + 
  facet_wrap(vars(Year)) + 
  theme_minimal() + 
  labs(x = "Acuity Score", y = "Empirical Logit", shape = "Score") + 
  ggtitle("Empirical Logit by Calculated Score, Year")

yr_cci_plot <- readmit_yr_cci %>% na_if(-Inf)
ggplot(yr_cci_plot, aes(x = Value, y = logit.Readmit, col= as.factor(Year))) + 
  geom_point(alpha = 0.4, size = 3) + geom_line() + 
  theme_minimal() + 
  labs(x = "CCI Score", y = "Empirical Logit", col = "Year") + 
  ggtitle("Empirical Logit by CCI Score, Year")

yr_lace_plot <- readmit_yr_lace %>% na_if(-Inf)
ggplot(yr_lace_plot, aes(x = Value, y = logit.Readmit, col= as.factor(Year))) + 
  geom_point(alpha = 0.4, size = 3) + geom_line() + 
  theme_minimal() + 
  labs(x = "LACE Score", y = "Empirical Logit", col = "Year") + 
  ggtitle("Empirical Logit by LACE Score, Year")

yr_hos_plot <- readmit_yr_hos %>% na_if(-Inf)
ggplot(yr_hos_plot, aes(x = Value, y = logit.Readmit, col= as.factor(Year))) + 
  geom_point(alpha = 0.4, size = 3) + geom_line() + 
  theme_minimal() + 
  labs(x = "HOSP Score", y = "Empirical Logit", col = "Year") + 
  ggtitle("Empirical Logit by HOSPITAL Score, Year")
```
  
### Appendix C: Demographic EDA Tables, Plots (#AppendixC)  
```{r appendc_cci}
readmit_cci_gen %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by CCI Score, Gender", digits=3,
      col.names = c("CCI Score", "Gender", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T) %>%
  collapse_rows(columns=0:1, valign="top")

readmit_cci_re %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by CCI Score, Race/Ethnicity", digits=3,
      col.names = c("CCI Score", "Race/Ethnicity", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T) %>%
  collapse_rows(columns=0:1, valign="top")

readmit_cci_ins %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by CCI Score, Insurance", digits=3,
      col.names = c("CCI Score", "Insurance", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T) %>%
  collapse_rows(columns=0:1, valign="top")

cci_gen_plot <- readmit_cci_gen %>% na_if(-Inf)
ggplot(cci_gen_plot, aes(x = CCI, y=logit.Readmit, shape=Value, label=CCI)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) +
  geom_text() + 
  labs(x = "CCI Score", y = "Empirical Logit", shape = "Gender") + 
  theme_minimal() + ggtitle("Empirical Logit by CCI Score, Gender")

cci_re_plot <- readmit_cci_re %>% na_if(-Inf)
ggplot(cci_re_plot, aes(x = CCI, y=logit.Readmit, shape=Value, label=CCI)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) + 
  geom_text() + 
  labs(x = "CCI Score", y = "Empirical Logit", shape = "Race/Ethnicity") + 
  theme_minimal() + ggtitle("Empirical Logit by CCI Score, Race/Ethnicity")

cci_ins_plot <- readmit_cci_ins %>% na_if(-Inf)
ggplot(cci_ins_plot, aes(x = CCI, y=logit.Readmit, shape=Value, label=CCI)) + 
  geom_point(alpha = 0.3, size = 5) + geom_line(alpha = 0.3) + 
  geom_text() + 
  labs(x = "CCI Score", y = "Empirical Logit", shape = "Insurance") + 
  theme_minimal() + ggtitle("Empirical Logit by CCI Score, Insurance")
```

```{r appendc_lace}
readmit_lace_gen %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by LACE Score, Gender", digits=3,
      col.names = c("LACE Score", "Gender", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T) %>%
  collapse_rows(columns=0:1, valign="top")

readmit_lace_re %>% 
  select(!Demo) %>%
  kbl(caption = "Readmission Empirical Statistics by LACE Score, Race/Ethnicity", digits=3,
      col.names = c("LACE Score", "Race/Ethnicity", "Mean Age", "N", "Readmit No.", "Readmit Prop", "Readmit Odds", "Readmit Logit")) %>%
  kable_minimal(full_width = F) %>%
  column_spec(1, bold=T) %>%
  collapse_rows(columns=0:1, valign="top")


```


```{r appendc_hos}


```


### Appendix D:  (#AppendixD)




***




